Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-17 sas2015/content/background.tex
squishing a single word to get half a page of space
text squeezing

\section{Background}\label{sec:bg}
%The purpose of the correlated-calls analysis is to solve IFDS problems more precisely than using the standard IFDS algorithm by ruling out some infeasible paths. The correlated-calls analysis works by transforming an IFDS problem to an IDE problem, solving the IDE problem, and transforming the IDE result to a solution to the original IFDS problem. 
This section defines basic terminology and presents the IFDS and IDE algorithms.
%\ftodo{
  %Shall we add a sentence saying that readers familiar with these algorithms may skip this section?
%}

@@

The IDE algorithm~\cite{sagiv1996precise} extends IFDS to
\textit{interprocedural} \textit{distributive} \textit{environment}
problems. An \textit{environment} problem is an analysis whose data-flow
lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice
$L$ of finite height, ordered pointwise. Like IFDS, IDE requires the data-flow functions to be distributive.

>>>>

\section{Background}\label{sec:bg}
%The purpose of the correlated-calls analysis is to solve IFDS problems more precisely than using the standard IFDS algorithm by ruling out some infeasible paths. The correlated-calls analysis works by transforming an IFDS problem to an IDE problem, solving the IDE problem, and transforming the IDE result to a solution to the original IFDS problem. 
This section defines terminology and presents the IFDS and IDE algorithms.
%\ftodo{
  %Shall we add a sentence saying that readers familiar with these algorithms may skip this section?
%}

@@

The IDE algorithm~\cite{sagiv1996precise} extends IFDS to
\textit{interprocedural} \textit{distributive} \textit{environment}
problems. An \textit{environment} problem is one whose data-flow
lattice is the lattice $\textsf{Env}(D,L)$ of maps from a finite set $D$ to a meet semilattice
$L$ of finite height, ordered pointwise. Like IFDS, IDE requires the data-flow functions to be distributive.

### 2015-03-17 sas2015/content/intro.tex
tweaks to save space
text squeezing

The remainder of this paper is organized as follows.
%
Section~\ref{sec:MotivatingExample} presents a motivating example.
%
Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
%
Section~\ref{sec:cca} presents the correlated-calls transformation
and sketches a proof of its correctness%
\footnote{
  Detailed proofs of our lemmas and theorems can be found in
  the appendix.
}.
%
Our implementation is discussed in Section~\ref{sec:Evaluation}.
%
Related work is discussed in Section~\ref{sec:Related}.
%
Finally, conclusions and directions for future work are presented in Section~\ref{sec:Conclusions}.

>>>>

The remainder of this paper is organized as follows.
%
Section~\ref{sec:MotivatingExample} presents a motivating example.
%
Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
%
Section~\ref{sec:cca} presents the correlated-calls transformation,
sketches a proof of its correctness,%
\footnote{
  Detailed proofs of our lemmas and theorems can be found in
  the appendix.
} and discusses our implementation.
%
%Our implementation is discussed in Section~\ref{sec:Evaluation}.
%
Related work is discussed in Section~\ref{sec:Related}.
%
Finally, Section~\ref{sec:Conclusions} presents conclusions and directions for future work.
